The LSST-DESC 3x2pt Tomography Optimization Challenge

### 2021-04-14 paper/paper.tex
more text on overlap

For comparison, we also show results using all six LSST bands, $ugrizy$; these could not be used
with the metacalibration method. The improvement in the sharpness of the bins is noticeable but not large,
and does not translate into large increases in the figures of merit: the DETF score for CosmoDC2
is 169.7, barely higher than the score for $griz$, and this is also true for other metrics.   While this is only a general indication and not a thorough exploration, it is encouraging.

>>>>

For comparison, we also show results using all six LSST bands, $ugrizy$; these could not be used
with the metacalibration method. The improvement in the sharpness of the bins is noticeable but not large.
We quantify this in Figure \ref{fig:overlap}, which shows the fraction of objects that are in ambiguous
redshift slices, defined as objects in redshift ranges where there are more objects assigned to another 
tomographic bin.  The total fraction of such objects is also shown. This illustrates how adding the $g$ band 
improves the assigment
for almost every pair of bins, and reduce the ambiguous fraction by a factor of three to the 
point where a significant majority of galaxies are clearly assigned.  Further adding the remaining $u$ and $y$
bands improves the assignment in a way that is smaller in both relative and absolute terms.
This latter addition also does not translate into large increases in the figures of merit: the 
DETF score for CosmoDC2 is 169.7, barely higher than the score for $griz$, and this is also true for other 
metrics.   While this is only a general indication and not a thorough exploration, it is encouraging.

\begin{figure*}[htbp]
% \centering
\includegraphics[width=0.9\linewidth]{results/nzoverlap_dc2_funbins.pdf}
\caption{The fraction of total objects assigned to each tomographic bin that are ambiguously assigned, for 
the \textsc{funbins} tomograph method and three choices of bands.  The $x$- and $y$-axes 
show tomographic bin indices, 
and the color represents the fraction of objects (compared to the total number in the challenge) that are 
at redshifts dominated by different tomographic to the ones they are assigned.
The total-overlap figure gives the total fraction of objects
that are ambiguous over all bins, and is the sum of all the values.}
\label{fig:overlap}
\end{figure*}
